% !TEX program = xelatex
\documentclass[11pt,a4paper]{article}
\usepackage[a4paper,margin=2cm]{geometry}
\usepackage{fontspec}
\usepackage{microtype}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{xcolor}
\usepackage{csquotes}
\usepackage{longtable}

% --- typography\&links ---
\setmainfont{Latin Modern Roman}
\setsansfont{Latin Modern Sans}
\hypersetup{colorlinks=true, linkcolor=black, urlcolor=blue!50!black, pdfauthor={Léopold Monjoie}, pdftitle={Curriculum Vitae}}
\titleformat*{\section}{\large\bfseries}

% --- compact lists ---
\setlist[itemize]{topsep=2pt,itemsep=2pt,parsep=0pt}
\setlist[enumerate]{topsep=2pt,itemsep=2pt,parsep=0pt}

% --- macros ---
\input{macros_cv.tex}

% --- header ---
\begin{document}
{\Large \textbf{L\'eopold Monjoie}}\\[2pt]
Postdoctoral Researcher in Economics\\
Aalto University, Helsinki, Finland\\
\href{mailto:leopold.monjoie@example.com}{leopold.monjoie@example.com} \;|\; \href{https://leopoldmonjoie.com}{leopoldmonjoie.com} \;|\; \href{https://scholar.google.com/}{Google Scholar}

\vspace{0.6em}\hrule\vspace{0.8em}

% --- research fields / interests ---
\cvsection{Fields}
Industrial Organization; Mechanism Design; Energy  \&  Environmental Economics; Electricity Markets.

% --- appointments ---
\cvsection{Appointments}
\cventry{Aalto University}{Postdoctoral Researcher}{Helsinki, Finland}{2025--}{Projects with Prof. Matti Liski; capacity markets; dynamic pricing.}
\cventry{Université Paris-Dauphine}{Teaching Fellow}{Paris, France}{2021--2024}{Microeconomics, Industrial Organization.}

% --- education ---
\cvsection{Education}
\cventry{Université Paris-Dauphine}{Ph.D. Economics}{Paris, France}{2019--2025}{Thesis: \emph{Designing Markets for Reliability with Incomplete Information}. Supervisor: Fabien Roques.}
\cventry{[Institution]}{M.Sc. Economics}{[City, Country]}{[Year]}{}

% --- publications \& working papers ---
\cvsection{Publications  \&  Working Papers}
\begin{longtable}{@{}p{1cm}p{14cm}@{}}
[WP] \& Monjoie, L. (2025). \emph{Designing Markets for Reliability with Incomplete Information}. Job Market Paper. Available at: \href{https://leopoldmonjoie.com/files/monjoie_jmp.pdf}{link}. \\
% [JPE] \& Doe, J. and Monjoie, L. (2024). Title. \emph{Journal Name}. \doi{10.xxxx/xxxxx}. \\
\end{longtable}

% --- research in progress ---
\cvsection{Research in Progress}
\begin{itemize}
  \item Capacity-contingent nonlinear pricing under redistributive concerns.
  \item Bundling with adverse selection in dynamic electricity tariffs.
\end{itemize}

% --- grants / awards ---
\cvsection{Grants \& Awards}
\begin{itemize}
  \item [2024] Award / Grant Name, Organization.
\end{itemize}

% --- talks ---
\cvsection{Talks    \&    Conferences}
\begin{itemize}
  \item EAERE (2024); CEEM; ADRES; Aalto Applied Micro; etc.
\end{itemize}

% --- teaching ---
\cvsection{Teaching}
\begin{itemize}
  \item Microeconomics (UG/PG); Industrial Organization; Problem sets; Exam design.
\end{itemize}

% --- skills ---
\cvsection{Skills}
\cvitem{Methods}{Mechanism design, IO, welfare analysis}
\cvitem{Tools}{MATLAB, LaTeX, Python, Stata}
\cvitem{Languages}{French (native), English (professional), Finnish (beginner)}

% --- service ---
\cvsection{Service}
Referee service, seminar organization (Helsinki/Aalto Environmental Economics Seminar), etc.

\end{document}